Understanding domestic abuse

### 2019-07-23 JeS_fields.tex
Minor typos in summary

We have 3 core objectives.

@@

Concern about domestic abuse is widespread, and it is rightly identified as a serious societal issue affecting the lives of people from all walks of life. However, the true extent of the problem is still often underestimated, and hard to comprehend: 2 million adults in England and Wales (7.9\% of women and 4.2\% of men) reported to have experienced some form of domestic abuse in the year ending 2018 March \cite{ONS}, and 41\% of all women murdered in England and Wales in the same period were victims of domestic homicide. The long-lasting, damaging effects of domestic abuse are not limited to the direct target of abuse, but also has serious developmental implications for children witnessing the abuse. Illustrating the extent of the societal harm caused by domestic abuse, the economic cost of domestic abuse in England and Wales between April, 2016 and March, 2017 was estimated to be as high as \pounds 66 billion, which primarily reflects the cost of missed work days, health costs, and the reduced quality of life for survivors \cite{costs}.

>>>>

We have 4 core objectives.

@@

Concern about domestic abuse is widespread, and it is rightly identified as a serious societal issue affecting the lives of people from all walks of life. However, the true extent of the problem is still often underestimated, and hard to comprehend: 2 million adults in England and Wales (7.9\% of women and 4.2\% of men) reported experiencing some form of domestic abuse in the year ending 2018 March \cite{ONS}, and 41\% of all women murdered in England and Wales in the same period were victims of domestic homicide. The long-lasting, damaging effects of domestic abuse are not limited to the direct victim of abuse, but also has serious developmental implications for children witnessing the abuse. Illustrating the extent of the societal harm caused by domestic abuse, the economic cost of domestic abuse in England and Wales between April, 2016 and March, 2017 was estimated to be as high as \pounds 66 billion, which primarily reflects the cost of missed work days, health costs, and the reduced quality of life for survivors \cite{costs}.
